Designing Types for R, Empirically

### 2020-05-14 paper/main.tex
evaluation organization
Add a few lines about R-dyntrace

In this section, we will describe our approach to data collection and
analysis through \typetracer, a dynamic analysis built in the \rdt
framework.  We will then describe the process by which we distill the rich
information we collect with \typetracer to more digestible ``types'', though
we discuss the precise details of our type annotation language in
Section~\ref{sec:types}.  Finally, we discuss \contractr, a package built in
R which supports our type language and can generate and check contracts for
function types.

@@

@@

%
%
\subsubsection{Subsumed Checks}

%
%
%
%
\subsection{Large-Scale Evaluation}
\label{subsec:eval}

@@

>>>>

In this section, we will describe our approach to data collection and
analysis through \typetracer, a dynamic analysis built in the \R-dyntrace
framework.  We will then describe the process by which we distill the rich
information we collect with \typetracer to more digestible ``types'', though
we discuss the precise details of our type annotation language in
Section~\ref{sec:types}.  Finally, we discuss \contractr, a package built in
R which supports our type language and can generate and check contracts for
function types.

%
\subsection{R-dyntrace}
R-dyntrace is a framework for performing dynamic analysis of R. It was designed
and used previously for a large-scale study of laziness in R~\cite{oopsla19} It
is an instrumented R Virtual Machine based on GNU-R version 3.5.0. It exposes
hooks from key points inside the R interpreter to which user defined callbacks
can be attached for gathering information about the program state at those
points. This information can be used to generate detailed program traces for
online or offline analysis. R-dyntrace provides hooks for function entry and
exit, S3/S4 dispatch, non-local jumps (because of longjumps in the R interpreter
on exceptions and other non-local returns), promise creation and forcing,
variable definition and mutation and garbage collection. garbage collection
entry and exit, function entry and exit.

@@

\AT{Aviral}

@@

%
%
%
%
\subsection{Evaluation of Types from Traces}
\label{subsec:eval}

\AT{Me}

@@

%
%
%
%
\subsection{Usefulness of the Type Checking Framework}

\AT{Filip}
